---
title: "Errata"
subtitle: "On Coppock, Hill and Vavreck (2020), *Science Advances* 6(36)"
format:
  pdf:
    output-file: coppock_hill_vavreck_2020_errata.pdf
    geometry: margin=1in
    fontsize: 11pt
    include-in-header:
      text: |
        \usepackage{caption}
        \captionsetup{labelformat=empty}
        \usepackage{float}
        \floatplacement{table}{H}
        \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

out <- function(f) read_csv(here("maintained", "output", f), show_col_types = FALSE)

text_numbers <- out("text_in_text_numbers.csv")
descriptive  <- out("text_descriptive_claims.csv")
table_1      <- out("table_1_meta_regression.csv")
table_s2     <- out("table_s2_heterogeneity.csv")
repeat_ads   <- out("text_repeat_ad_homogeneity.csv")

txt <- function(name) {
  value <- text_numbers$value[text_numbers$claim == name]
  stopifnot(length(value) == 1)
  value
}

computed <- function(claim) {
  value <- descriptive$computed[descriptive$claim_id == claim]
  stopifnot(length(value) == 1)
  value
}

s2_value <- function(estimand, dv, column) {
  value <- table_s2[[column]][table_s2$estimand == estimand & table_s2$dv == dv &
                                table_s2$method == "DL (published)"]
  stopifnot(length(value) == 1)
  value
}

cate_vote_choice_p <- s2_value("cates", "Vote Choice", "p.value")

general_election <- table_1$estimate[table_1$model == "Candidate favorability (1)" &
                                       table_1$term == "general_d"]

partisanship <- table_1 |> filter(term %in% c("democrat_d", "independent_d"))

# R11, 2026-09-19. Each entry below is asked what its corrected cell was the WARRANT for:
# which sentence a referee would have said rests on it, and whether that sentence survives
# the corrected value. Every benchmark the notes quote is computed here rather than typed,
# so a re-render moves it with the deposited data.

# Entry 1. The three homogeneity tests the article does not reject. The published 0.96 was
# the only one of the four no conventional threshold could touch.
homogeneity_not_rejected <- sort(c(
  s2_value("sates", "Favorability", "p.value"),
  s2_value("sates", "Vote Choice", "p.value"),
  cate_vote_choice_p
))
cate_vote_choice_tau <- s2_value("cates", "Vote Choice", "tau")

# Entry 3. The set a significance filter would leave, which is what the passage inventories.
weekly_favorability <-
  out("figure_1_sate_time_series.csv") |>
  filter(dv == "Favorability", est_type == "Weekly estimates")
significant_weekly <- weekly_favorability |> filter(conf.low > 0 | conf.high < 0)

# Entry 4. No partisanship cell reaches even 1.1 standard errors from zero, which is the
# benchmark that says the claim the sentence supports survives its corrected count.
partisan_max_ratio <- max(abs(partisanship$estimate) / partisanship$std.error)

# Entry 5. The four counts the sentence gives are a partial inventory of the 59
# advertisement-week experiments, and correcting them resizes the residual category.
deployments_named <- sum(map_dbl(
  c("n_deployments_anti_trump", "n_deployments_anti_clinton",
    "n_deployments_pro_clinton", "n_deployments_pro_trump"),
  txt))
deployments_other <- txt("n_ad_week_deployments") - deployments_named

# Entry 6. Table S1 is the stated roster, and it prints one cell per advertisement-week that
# has a distinct title, so it reaches neither the 49 advertisements nor the 59 experiments.
table_s1 <- out("table_s1_ad_list.csv")
table_s1_cells <-
  table_s1 |>
  select(-date_formatted) |>
  pivot_longer(everything()) |>
  filter(!is.na(value)) |>
  pull(value)

# Entry 7. The corrected list is Figure S1's panel set, name for name, so section A's list
# is the stated definition of what that figure shows.
figure_s1 <- out("figure_s1_repeat_ads.csv")
stopifnot(identical(sort(unique(figure_s1$ad_title)), sort(unique(repeat_ads$ad_title))))

# Entry 8. What the manipulation check is the warrant for is the contrast with the control
# groups, and the corrected low end is what that contrast is exposed on.
manip_ratio <- txt("manip_check_treated_min") / txt("manip_check_control_max")

# The article's "more than +0.5 points" is a lower bound on the largest positive
# estimate, so the corrected bound is that estimate rounded down to the same precision.
largest_october <- computed("desc_large_positive_october")
october_bound <- floor(largest_october * 10) / 10

# The published list quotes each title with the comma inside the quotation marks and none
# after the last, so the corrected list is built the same way.
repeat_ad_titles <- sort(unique(repeat_ads$ad_title))
repeat_ad_list <- str_c(
  str_c('"', head(repeat_ad_titles, -1), ',"', collapse = " "),
  ' "', tail(repeat_ad_titles, 1), '"'
)

spell <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight",
             "nine", "ten", "eleven", "twelve")
  stopifnot(n >= 1, n <= length(words))
  words[n]
}
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. `location` carries the part of the article the entry sits in, which is what
# the "Published, ..." line above each quotation prints.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
#
# claim_ids names the ground-truth rows an entry corrects, semicolon-separated, so that
# "is this finding published?" is a query rather than a judgment. An entry that corrects
# several numbers at once lists every one of them: entry 2 carries the Table 1 battleground
# cell alongside the coefficient the sentence misstates, because the table is reprinted with
# that cell fixed. It is empty where an entry has no ground-truth row at all. Every id
# listed here is checked against the ground truth by build_ground_truth.R.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "quantity", "pipeline", "full",
  "The CATE homogeneity p-value for vote choice is misstated by a factor of ten",
  "published, Results",
  "For the set of conditional average treatment effects (CATEs), P values are 0.0002 and [[0.96]].",
  str_glue("For the set of conditional average treatment effects (CATEs), P values are 0.0002 and [[{sprintf('%.4f', cate_vote_choice_p)}]]."),
  str_glue(
    "Table S2 of the same article reports {sprintf('%.4f', cate_vote_choice_p)} for this ",
    "test, which is what the deposited code produces. The test still fails to reject the ",
    "null of homogeneity at the 5 per cent level, so the sentence two paragraphs later, that ",
    "homogeneity is not rejected in three of four opportunities, stands as published.",
    "\n\n",
    "What the correction changes is how much weight that sentence can carry. The three tests ",
    "the article does not reject now run ",
    "{str_c(sprintf('%.3f', homogeneity_not_rejected), collapse = ', ')}, so all three sit ",
    "between 0.05 and 0.10 and the count would be none of four at the 10 per cent level. The ",
    "published 0.96 was the only one of the four p-values no conventional threshold could ",
    "touch. The passage does not rest on the tests: it says so itself, declining to affirm ",
    "the null and relying instead on the random-effects estimate of the true standard ",
    "deviation of the effects, which for these CATEs is ",
    "{sprintf('%.1f', 100 * cate_vote_choice_tau)} percentage points on vote choice and is ",
    "unchanged."),
  "results_s2_cate_vc_p",

  2, "quantity", "pipeline", "full",
  "The general election coefficient disagrees with Table 1",
  "published, Results",
  "On average, general election advertisements move candidate favorability by [[0.121 scale points]] more than primary advertisements, although the estimate is not precise enough to achieve statistical significance.",
  str_glue("On average, general election advertisements move candidate favorability by [[{sprintf('%.3f', general_election)} scale points]] more than primary advertisements, although the estimate is not precise enough to achieve statistical significance."),
  str_glue(
    "Table 1 of the same article prints {sprintf('%.3f', general_election)} in this cell.",
    "\n\n",
    "Table 1 also prints the model 1 battleground coefficient as $-0.00$, where the ",
    "deposited code gives ",
    "${sprintf('%.3f', table_1$estimate[table_1$model == 'Candidate favorability (1)' & table_1$term == 'battleground_d'])}$; ",
    "the facing text quotes its magnitude correctly as 0.008. The table is reprinted below ",
    "with that cell at the three decimals the rest of the column carries. Every other cell ",
    "is unchanged.",
    "\n\n",
    "The sentence carries one number downstream, three sentences later: the upper bound of ",
    "the 95 per cent interval for the same difference, which the article gives as about 0.25. ",
    "Computed from the corrected coefficient it is ",
    "{sprintf('%.3f', table_1$conf.high[table_1$model == 'Candidate favorability (1)' & table_1$term == 'general_d'])}, ",
    "so the bound and the reading built on it, that any heterogeneity by election phase is ",
    "too small to matter politically, stand as published."),
  "results_general_election_coefficient;table_1_m1_battleground_d_est",

  3, "quantity", "pipeline", "full",
  "No positive estimate in the study exceeds half a scale point",
  "published, Results",
  "...one large positive result toward the end of the campaign in October ([[more than +0.5 points]]), and two other negative results in October.",
  str_glue("...one large positive result toward the end of the campaign in October ([[more than +{sprintf('%.1f', october_bound)} points]]), and two other negative results in October."),
  str_glue(
    "The largest positive weekly estimate anywhere in the study is ",
    "{sprintf('%.3f', largest_october)}, on the advertisement \"Example\" in the week of 31 ",
    "October. The passage's point, that a significance filter applied to these experiments ",
    "would leave a handful of results that look large, is unaffected.",
    "\n\n",
    "The filter is what the corrected number is the warrant for, and it can be applied: of ",
    "the {nrow(weekly_favorability)} weekly favorability experiments, ",
    "{spell(nrow(significant_weekly))} have an interval excluding zero, and they run from ",
    "${sprintf('%.3f', min(significant_weekly$estimate))}$ to ",
    "{sprintf('%.3f', max(significant_weekly$estimate))}. The passage names the four largest ",
    "of those {spell(nrow(significant_weekly))} in magnitude. So a filtered literature drawn ",
    "from this study would show a spread of about a fifth of the favorability scale, which is ",
    "the appearance of heterogeneity the passage is describing, and the corrected bound does ",
    "not soften it. The title of this entry says positive because the study's most extreme ",
    "estimate of either sign is ",
    "${sprintf('%.3f', min(significant_weekly$estimate))}$, the early May result the same ",
    "sentence describes as nearly $-0.5$."),
  "desc_large_positive_october",

  4, "description", "pipeline", "full",
  "Standard errors do not exceed the coefficients in every partisanship cell",
  "published, Results",
  "Turning first to features of receiver, we see that the differences in treatment response across Democrats, Independents, and Republicans are small, [[with SEs greater than coefficients]].",
  str_glue("Turning first to features of receiver, we see that the differences in treatment response across Democrats, Independents, and Republicans are small, [[with SEs greater than coefficients in {computed('desc_partisan_ses_exceed_coefficients')} of the {nrow(partisanship)} cells]]."),
  str_glue(
    "The two exceptions are the Democratic respondent coefficients in columns 1 and 3 of ",
    "Table 1, and the second is visible on the printed page: 0.011 with a standard error of ",
    "0.010. Neither coefficient is distinguishable from zero, so the claim the sentence ",
    "supports, that treatment response does not differ by respondent partisanship, is ",
    "unaffected.",
    "\n\n",
    "The count is a proxy and the quantity behind it is the better warrant: across all ",
    "{nrow(partisanship)} cells the largest ratio of a coefficient to its own standard error ",
    "is {sprintf('%.2f', partisan_max_ratio)}, so no partisanship difference in the table ",
    "reaches even 1.1 standard errors from zero. Six of eight is what the published sentence ",
    "would have read as a weaker version of its own claim; the ratio says the claim is as ",
    "strong as the sentence makes it."),
  "desc_partisan_ses_exceed_coefficients",

  5, "quantity", "pipeline", "full",
  "The advertisement counts in section A disagree with the main text",
  "published, supplementary materials, section A",
  "Including the ads we deployed more than once, we tested [[28]] ads that attacked Trump, [[nine]] attacks on Clinton, [[nine]] Clinton promotional ads, and three promotional Trump ads.",
  str_glue("Including the ads we deployed more than once, we tested [[{txt('n_deployments_anti_trump')}]] ads that attacked Trump, [[{txt('n_deployments_anti_clinton')}]] attacks on Clinton, [[{txt('n_deployments_pro_clinton')}]] Clinton promotional ads, and three promotional Trump ads."),
  str_glue(
    "Counted as the section says, over advertisement-week deployments rather than distinct ",
    "advertisements, the breakdown is {txt('n_deployments_anti_trump')}, ",
    "{txt('n_deployments_anti_clinton')}, {txt('n_deployments_pro_clinton')} and ",
    "{txt('n_deployments_pro_trump')}, which is exactly what the main text states. Counted ",
    "over distinct advertisements it is 24, 11, 6 and 3. The published breakdown matches ",
    "neither.",
    "\n\n",
    "The four counts are a partial inventory, and correcting them resizes what is left. They ",
    "now sum to {deployments_named} of the {txt('n_ad_week_deployments')} ",
    "advertisement-week experiments, leaving {deployments_other} for the promotional ",
    "advertisements for other primary candidates the next sentence calls the remainder, ",
    "where the published counts left 10. Nothing estimated in the article is computed from ",
    "this split: it is an inventory of the treatments, and its warrant is that a reader can ",
    "reconcile section A with the main text, which the published version does not allow."),
  "appendix_a_n_anti_trump;appendix_a_n_anti_clinton;appendix_a_n_pro_clinton",

  6, "quantity", "pipeline", "full",
  "The number of unique advertisements in section A disagrees with the abstract",
  "published, supplementary materials, section A",
  "Table S1 shows the name and target of the [[50]] unique advertisements and the week they were deployed.",
  str_glue("Table S1 shows the name and target of the [[{txt('n_unique_ads')}]] unique advertisements and the week they were deployed."),
  str_glue(
    "The deposited data hold {txt('n_unique_ads')} campaign advertisements plus the placebo, ",
    "and the abstract's {txt('n_unique_ads')} is right. The abstract, the introduction and ",
    "the discussion all say {txt('n_unique_ads')}, so section A was the one place in the ",
    "paper that said 50.",
    "\n\n",
    "The sentence also defines Table S1, and the corrected number does not reach it. That ",
    "table prints one cell per advertisement-week with a distinct title, which is ",
    "{length(table_s1_cells)} cells carrying {n_distinct(table_s1_cells)} distinct names, so ",
    "a reader who counts it recovers neither the {txt('n_unique_ads')} advertisements nor the ",
    "{txt('n_ad_week_deployments')} experiments. Two of the {txt('n_unique_ads')} ",
    "advertisements share the title \"Sacrifice\", the target Trump and the week of 5 ",
    "September, and the table has no way to show them apart. The shortfall is in the table's ",
    "presentation and not in the study: both advertisements are in the deposited data and ",
    "both are in every estimate the article reports."),
  "appendix_a_n_unique_ads",

  7, "label", "pipeline", "full",
  "Section A names eight advertisements shown in multiple weeks",
  "published, supplementary materials, section A",
  "Some advertisements ([[\"America,\" \"Love/Kindness,\" \"Man of People,\" \"Mirrors,\" \"Quotes,\" \"Real Life,\" \"Role Model,\" \"Speak\"]]) were shown in multiple weeks, enabling us to estimate how the effect of the same advertisement may vary with the changing electoral context.",
  str_glue("Some advertisements ([[{repeat_ad_list}]]) were shown in multiple weeks, enabling us to estimate how the effect of the same advertisement may vary with the changing electoral context."),
  str_glue(
    "\"Man of People\" was fielded once, in the week of 14 March. Section B and Figure S1 ",
    "both use the correct count of {nrow(repeat_ads)}.",
    "\n\n",
    "The list is not a label on the sentence: it is the stated roster of what Figure S1 ",
    "shows. That figure carries one panel per advertisement fielded in more than one week, ",
    "and its {spell(n_distinct(figure_s1$ad_title))} panels are the corrected ",
    "{spell(nrow(repeat_ads))} names exactly, in order. The published eighth name therefore ",
    "promises ",
    "a panel that is not in the figure, and section B, two pages later, already says seven. ",
    "The analysis is unaffected because the figure and the tests behind it were always the ",
    "correct {spell(nrow(repeat_ads))}: what was wrong was the only place a reader is told which ",
    "advertisements they are."),
  "appendix_a_n_repeat_ads_named",

  8, "quantity", "pipeline", "full",
  "The manipulation check range is one point narrow at each end",
  "published, Materials and Methods",
  "Tiny fractions of the control groups claimed to have seen campaign advertisements (2 to 4%) compared with large majorities of the treatment groups ([[92 to 95%]]).",
  str_glue("Tiny fractions of the control groups claimed to have seen campaign advertisements (2 to 4%) compared with large majorities of the treatment groups ([[{sprintf('%.0f', 100 * txt('manip_check_treated_min'))} to {sprintf('%.0f', 100 * txt('manip_check_treated_max'))}%]])."),
  str_glue(
    "Across the ten waves in which the manipulation check was asked, the unweighted share of ",
    "treated respondents reporting a campaign advertisement runs from ",
    "{sprintf('%.1f', 100 * txt('manip_check_treated_min'))} to ",
    "{sprintf('%.1f', 100 * txt('manip_check_treated_max'))} per cent, which is what the ",
    "deposited script written for this sentence computes. Weighting by the survey weights ",
    "widens the range further, to 90.2 to 95.9 per cent. The control group range is correct ",
    "as published.",
    "\n\n",
    "The sentence is the article's warrant that treatments were delivered as intended, and ",
    "what carries that claim is the low end rather than the range. Correcting it moves the ",
    "worst wave down by one point, to ",
    "{sprintf('%.1f', 100 * txt('manip_check_treated_min'))} per cent, which is still ",
    "{sprintf('%.0f', manip_ratio)} times the highest rate any control group reported. ",
    "Delivery is not in question in any wave."),
  "methods_manip_treated_min;methods_manip_treated_max",

  9, "typographic", "remaster", "brief",
  "\"treatmen\" for \"treatment\"",
  "published, Materials and Methods",
  "OLS is a consistent estimator of the average [[treatmen]] effect (ATE) under our design (35).",
  "OLS is a consistent estimator of the average [[treatment]] effect (ATE) under our design (35).",
  paste(
    "A dropped letter, in the sentence that names the estimand. The article spells the term",
    "correctly everywhere else, including in the sentence immediately before this one. Found",
    "by the remaster, which carries the published text across word by word. No quantity is",
    "involved, so the question this note asks of the other eight entries, what the corrected",
    "value was the warrant for, does not arise. What the correction restores is that the",
    "sentence defining the estimand spells it, which is the one sentence in the article where",
    "the term is doing definitional work rather than referring back."),
  ""
) |>
  mutate(across(c(title, published, corrected, note, claim_ids), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one.
emit <- function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published, "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
}
```

This note lists `r spell(nrow(entries))` errors in "The small effects of political advertising are small regardless of context, message, sender, or receiver: Evidence from 59 real-time randomized experiments," published in *Science Advances* 6(36), doi [10.1126/sciadv.abc4046](https://doi.org/10.1126/sciadv.abc4046). **None of them changes a conclusion of the paper.** That is an adjudication rather than an assurance: each entry below was taken back to the sentence a referee would have said rests on it, and each note says what the corrected value is now the warrant for. The first eight are recorded because the numbers themselves are wrong and a reader who quoted them would be misled; the ninth is a dropped letter, recorded on the same principle.

Items 1 through 4 are in the main text, items 5 through 7 in section A of the supplementary materials, and items 8 and 9 in Materials and Methods. Every corrected value below is computed from the deposited replication archive ([10.7910/DVN/TN7KWR](https://doi.org/10.7910/DVN/TN7KWR)) at the time this document is rendered. The maintained code is at [github.com/active-maintenance-aec/coppock_hill_vavreck_2020](https://github.com/active-maintenance-aec/coppock_hill_vavreck_2020).

```{r entries-1-2, results="asis"}
walk(1:2, emit)
```


```{r table-1}
#| output: asis
# The table as the pipeline writes it, scaled to the page. Nothing but the width is
# touched: the cells come straight from maintained/output/table_1_meta_regression.tex.
table_1_tex <- read_lines(here("maintained", "output", "table_1_meta_regression.tex"))
table_1_tex <- str_replace(table_1_tex, fixed("\\begin{tabular}"),
                           "\\resizebox{\\linewidth}{!}{\\begin{tabular}")
table_1_tex <- str_replace(table_1_tex, fixed("\\end{tabular}"), "\\end{tabular}}")
cat(table_1_tex, sep = "\n")
```

\parbox{\linewidth}{\footnotesize\raggedright \textit{Note:} Table 1 as published, with the model 1 battleground coefficient printed to three decimals. Standard errors in parentheses; $*$ denotes $p < 0.05$. Estimated from the deposited replication archive by \texttt{maintained/table\_1\_meta\_regression.R}.}

```{r entries-3-8, results="asis"}
walk(3:max(entries$entry), emit)
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
